---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# gliefr

<!-- badges: start -->
<!-- badges: end -->

An R package to support analysis of GLEIF data.

## Installation


Install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Financial-Times/gleifr")
```
## Example

Download the latest LEI-CDF and RR-CDF files from [gleif.org](https://www.gleif.org/en/lei-data/gleif-golden-copy/download-the-golden-copy#/)

```{r read-data, eval=FALSE}
library(gliefr)

# Read in the files
entities <- read_gleif_entities_csv(file = "path/to/lei-cdf.csv")
relationships <- read_gleif_relationships_csv(file = "path/to/rr-cdf.csv")

```

Find the ultimate owner of legal entities with

```{r ultimate-parent, eval=FALSE}

ultimate_owners <- ultimate_parent(entities, relationships)

```

Find full documenation of the cleaned data set with
```{r docs, eval=FALSE}
?gleif_entities
?gleif_relationships

```
or the raw data documentation for [entities](https://www.gleif.org/en/about-lei/common-data-file-format/lei-cdf-format) and [relationships](https://www.gleif.org/en/about-lei/common-data-file-format/relationship-record-cdf-format).

## Data Notes

1. Having an LEI became a requirement for EU companies on 3rd Jan 2018. Unfortunately this means that there are very few entity and relationship registrations before that date.
2. Entities relationships can be "IS_DIRECTLY_CONSOLIDATED_BY", "IS_INTERNATIONAL_BRANCH_OF" (rare) or "IS_ULTIMATELY_CONSOLIDATED_BY". It is quite common for two entities to be both directly consolidated by and ultimately consolidated by. 
